---
title: "Cars Clustering"
author: "Floris Hol"
date: "3 May 2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
``` 

## Introduction Cars

Different cars have different speeds and stopping distances when kicking the 
brake. The developed app clusters cars based on these two variables using the
k-means clustering technique.

The user of the app can set the number of clusters to be created manually in
order to verify which number of clusters (centroids) shows the clearest 
distribution.




## Dataset

A native R dataset has been used for the purpose of building this app. A 
scatterplot shows the cars  on both axes before clustering:

```{r, cars, fig.cap="A scatterplot.", echo=FALSE}
plot(cars)
```




## K-means clustering

K-Means starts by randomly defining k centroids. From there, it works in 
iterative (repetitive) steps to perform two tasks:

- Assign each data point to the closest corresponding centroid, using the 
standard Euclidean distance. 

- For each centroid, calculate the mean of the values of all the points 
belonging to it. The mean value becomes the new value of the centroid.



## Go to the App

You can find the app here on my Github page:

https://mycarsclusteringapp.shinyapps.io/myApp/

